Sampling Strategies in Decisions from Experience

### 2022-03-02 manuscript.Rmd
Prelimary Draft Intro, Sec 1 & 2

The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the *properties* of the choice alternatives between which people can choose.
In fact, irrespective of their exact mathematical specification or computational implementation, decision models generally take as inputs information about a set of choice alternatives to return a subset thereof as outputs [@heOntologyDecisionModels2020].

Now, more formally, let us treat the choice alternatives as elements $c$ of the set $C$.
To each $c \in C$ is then assigned some information from the inputs and this information may be used by the mind to learn about the properties of the respective alternative.
Accordingly, decision making can be considered an information-processing problem which starts from the set $C$, containing all choice alternatives, and stops at a proper subset $C' \subset C$ with the inclusion map
$$
\begin{aligned}
  \iota : C' &\to C \\
  c &\mapsto c  \quad \forall c \in C'
\end{aligned}
\tag{1}
$$
[@jostMathematicalConcepts2015, p. 15], containing only the chosen alternatives.

Importantly, the information that is provided about the choice alternatives can come in many forms.
For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all relevant properties of the choice alternatives.
Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], the properties of the choice alternatives are latent---i.e., not described---and therefore not known with certainty, but they must be inferred from the consequences (hereafter: outcomes) that occurred when the alternatives were chosen in similar past decisions.
Although these distinct input forms may in principle carry the same information about a given set of choice alternatives, behavioral decision research has so far produced a large body of papers indicating that---if a quite general perspective is taken---there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a rare outcome is given more weight in the evaluation of a choice alternative than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same rare outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
Hereafter, these choice patterns are referred to as the as-if overweighting and underweighting of rare outcomes, respectively.

This paper uses the as-if underweighting of rare outcomes as a starting point for an inquiry into the sampling process upfront choices in DfE.
Essentially, it discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into *samples* (hereafter: sampling strategies) can produce distinct choice patterns in DfE---among them, the as-if underweighting of rare outcomes [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].

The rest of the paper is therefore structured as follows.
In the first brief section, a formal definition of DfE is provided.
In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices in DfE in terms of deviations from the principle of mathematical expectation.
In the section that follows, sampling strategies are treated.
<!-- Outline of the section -->
Thereafter, a simulation is presented in which the theoretical claims that are made in the preceding section are implemented in a computational model to simulate choice data in DfE.
The predictions of the model are summarized and fitted in CPT.
The paper closes with a summary and a conclusion.
Note that this paper, including the simulations and data analyses, is reproducible---materials and instructions can be found on the GitHub repository.

@@

Since there is an uncountable number of decisions people confront in the natural world, behavioral decision research routinely abstracts from decisions between particular choice alternatives, e.g., the choice between job offers, political parties to vote for, investment plans, and whatnot.
Rather, with the choice between at least two *prospects* (see below), it studies a case which is counterfactual in that it omits the many particularities of each decision, but retains in the form of prospects the fundamental properties that almost all choice alternatives are assumed to possess [@lopesThoughtsPsychologicalConcept1983].
These fundamental properties are considered the possible outcomes of a choice alternative (hereafter: $x_i$) and the probabilities with which these outcomes occur following the choice of the alternative (hereafter: $p_X(x_i)$).
Roughly speaking, then, all choice alternatives that can be fully described by their outcome-probability pairs $(x_i, p_X(x_i))$ are prospects (or: gambles), which are exclusively considered below.

Now, more formally, let the axiomatic definition of a prospect be that of a discrete random variable's distribution.
Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
Following the @kolmogorovFoundationsTheoryProbability1950 axioms, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
$$
\omega_i \in \{\omega_1, ..., \omega_n\} = \Omega
\; .
\tag{2}
$$ 
$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$ with each element $A \in P(\Omega) = \mathcal{F}$ being a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces. The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp. 2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra. For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].<!--Close footnote-->]
$P$ is a probability measure
$$
P: \mathcal{F} \to [0,1]
\; ,
\tag{3}
$$
which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
The random variable $X$ is the measurable function
$$
\begin{aligned}
  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
  \omega &\mapsto x
  \; ,
\end{aligned}
\tag{4}
$$
where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
An outcome's probability $p_X(x)$ is then provided by the probability measure
$$
P_X : \mathcal{F'} \to [0,1]
\tag{5}
$$
with 
$$
P_X(A' \in \mathcal{F'}) := P(X^{-1} \ A') = P(\{\omega: X(\omega) = x \in A'\})
\tag{6}
$$
[see @kolmogorovFoundationsTheoryProbability1950, p. 21-22].^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(X(\omega) = x)$.
Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
$$
C = \{P_{X_1}, ... , P_{X_k}\}
\tag{7}
$$
with each element $c \in C$ being a distribution $P_X$ of a random variable defined on its own probability space.
Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p_X(x_i)) \in \{(x_1, p_X(x_1)), ..., (x_n, p_X(x_n))\}$.

However, rarely in peoples' daily life, inputs take the form of explicit descriptions of all outcomes-probability pairs.
In such cases, people would make DfD, since the information from which the mind learns about the prospects are complete descriptions thereof.
Yet, rather often, people make DfE, where the mind can learn about the latent prospects only from a record of past experiences with them.
That is, people may have experienced the possible outcomes of a prospect when they themselves or others have made the same decision repeatedly in the past, and the record of experienced outcomes for this particular prospect is a rough description of a sample.
The mind may then infer from the relative frequency with which an outcome occurred in such a sample of past decisions its probability of occurrence following a future decision.

Now, more formally, let the sample of a prospect be a set of realizations of the respective random variable according to its distribution $P_X$.
That is, for the choice between $1, ..., k$ prospects, the inputs to DfE are generated by a set $S$ of stochastic processes
$$
S = \{X_{1t}, ... , X_{kt}\}
\tag{8}
$$
with $t \in \{1, ..., N\}$ denoting a sequence of independent and identically distributed (i.i.d.) random variables and $N$ denoting the length of the respective sequence [but see, e.g., @plonskyRelianceSmallSamples2015, where the i.i.d.-assumption is dropped].
So, given a stochastic process $s \in S$, the obtained realizations---i.e., the experienced outcomes---may be sequentially integrated into a sample of size $N$ or into multiple smaller samples.
Then, the samples so obtained can serve probabilistic inferences about the properties of the latent prospects in (7), the sets of outcome-probability pairs respectively.

Of course, the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950] apply to DfE and it follows that the accuracy of inferences from samples to latent prospects depend, ceteris paribus, on the size of the samples.
In fact, one explanation for the as-if underweighting of rare outcomes in DfE and the description-experience gap outlined in the introduction is that people rely on too small samples, which, due to the skewness of the binomial distribution, cause the relative frequencies with which rare outcomes occur in the samples to be smaller than their objective probabilities [@hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; see also @hertwigDecisionsExperienceWhy2010].
The invoked argument is then that what may appear as if people were underweighting rare outcomes relative to what would be warranted on the basis of their objective probabilities---following the principle of mathematical expectation---may in fact be consistent with an as-if overweighting relative to what would be warranted on the basis of the experienced relative frequencies [@foxDecisionsExperienceSampling2006].
Yet, it seems that the small size of samples in DfE provides just one and only a partial explanation for the description-experience gap [@hauDescriptionexperienceGapRisky2008; @hauDecisionsExperienceStatistical2010; @ungemachAreProbabilitiesOverweighted2009; see also @wulffMetaanalyticReviewTwo2018].
More so, despite the LLN, the gap need not narrow at all, even for ever increasing sample sizes that are fully taken into account.
Particularly, this paper discusses and demonstrates in a simulation how different strategies of sequentially generating outcomes and integrating them into samples interact with the LLN to produce distinct choice patterns in DfE---including the as-if underweighting of rare outcomes---that tend to stabilize as the sample size increases.
Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.

@@

...

@@

@@

For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.
We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
Table A1 in [Appendix 2][Appendix 2: Choice Problems] contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.

@@

>>>>

The human mind is a cognitive system that operates on inputs from an environment or memory, and in the domain of decision making, such inputs provide information about the choice alternatives between which people can choose.
In fact, irrespective of their exact specification, decision models generally take as inputs information about a set of choice alternatives, each possessing some defining *properties*, and returns a subset of chosen alternatives as outputs [@heOntologyDecisionModels2020].
Let us therefore treat the choice alternatives as elements $c$ of the set $C$, and decision making as an information-processing problem starting from $C$ and stopping at a proper subset $C' \subset C$ with the inclusion map
$$
\begin{aligned}
  \iota : C' &\to C \\
  c &\mapsto c  \quad \forall c \in C'
\end{aligned}
\tag{1}
$$
[cf. @jostMathematicalConcepts2015, p. 15].

Now, let a *prospect* be a choice alternative that possesses only two kinds of properties: the possible outcomes of the alternative and the probabilities with which these outcomes occur following its choice.
Importantly, the information that inputs provide about the properties of a prospect can come in different forms.
For example, in *decisions from description* (DfD), inputs take the form of explicit and complete descriptions of all outcomes and probabilities.
Yet, in *decisions from experience* [DfE, @hertwigDecisionsExperienceEffect2004], these properties are latent and therefore not known with certainty, but they must be inferred from the relative frequencies with which the outcomes occurred when the prospect was chosen in past decisions.
The inputs to DfE therefore take the form of samples.
Although these distinct input forms may in principle carry the same information about a given set of prospects, behavioral decision research has so far produced a large body of papers indicating that there are robust differences between the choices that are made in DfD and DfE, leading to the notion of the *description-experience gap* [@hertwigDescriptionexperienceGapRisky2009].
In one reading of the gap, empirical choice patterns indicate that in DfD people choose as if a small-probability outcome is given more weight in the evaluation of a prospect than would be objectively warranted by the principle of mathematical expectation; in turn, in DfE, ceteris paribus, people choose as if the same small-probability outcome is given less weight than would be warranted [e.g., @barronSmallFeedbackbasedDecisions2003; @hertwigDecisionsExperienceEffect2004; @weberPredictingRiskSensitivity2004; @erevAnomaliesForecastsDescriptive2017; see @wulffMetaanalyticReviewTwo2018, for a comprehensive meta-analytic review].
Hereafter, these choice patterns are referred to as the *as-if overweighting* and *as-if underweighting of rare outcomes*, respectively.

Similar to other behavioral phenomena that can be explained by the mind being sensitive to the composition of the samples on which it operates [see @fiedlerBewareSamplesCognitiveecological2000], the as-if underweighting of rare outcomes in DfE can be explained by the tendency to rely on small samples [see, e.g., @hertwigDecisionsExperienceEffect2004; @rakowBiasedSamplesNot2008; @wulffMetaanalyticReviewTwo2018].
That is, following from the laws of large numbers [LLN, see, e.g., @kolmogorovFoundationsTheoryProbability1950], the relative frequency with which a prospect's outcome occurs in a sample of infinite size converges almost surely to its objective probability.
In such a case, but also in the less strict case of large samples, then, the binomial distribution of each prospect's outcome can be approximated by a symmetric normal distribution [see @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015].
However, for small samples, the binomial distribution of small-probability outcomes is positive skewed, therefore causing the relative frequencies with which these outcomes occur in the sample to be smaller rather than larger than their latent objective probabilities.
Thus, small-probability outcomes tend to be underrepresented in small samples and might not occur at all.
As a consequence, were the mind to use the sampled relative frequencies of outcomes to infer their latent objective probabilities---without correction of sampling error---and to follow the principle of mathematical expectation, the reliance on small samples could explain the as-if underweighting of rare outcomes. 
Since the same line of reasoning applies would the mind approximate the principle of mathematical expectation by choosing the prospect that produced the greater sample mean, the following discussion focuses on choices in DfE that are based on comparisons of sampled means.
The relevance of making the inference about latent properties explicit, however, is addressed in the last section of this paper.

Now, this paper uses the outlined effect of small samples as a starting point for an inquiry into the sampling process upfront choices in DfE.
Specifically, in one paradigm used to study DfE, i.e., the sampling paradigm [see @weberPredictingRiskSensitivity2004], before making a single choice between prospects with latent properties, people can, as much as they want, sequentially sample the prospects' outcomes according to their objective probabilities.
Considering this paradigm, the current paper discusses how different strategies of sampling and integrating the prospects' outcomes (hereafter: *sampling strategies*) can produce distinct choice patterns in DfE by altering the number and size of the samples that are used by the mind to accumulate evidence over time [see @hillsInformationSearchDecisions2010, for the original formulation of this claim].
The paper proceeds as follows:
In the first section, a formal definition of DfE is provided.
In the subsequent section, cumulative prospect theory [CPT, @tverskyAdvancesProspectTheory1992; @wakkerAxiomatizationCumulativeProspect1993] is reviewed as a data model that can be used to describe choices between prospects in terms of deviations from the principle of mathematical expectation.
In the section that follows, using an evidence accumulation approach, different sampling strategies are discussed, how they produce distinct choice patterns in DfE, and how these patterns may be captured in the parameters of CPT.
Thereafter, a simulation is presented in which these sampling strategies are implemented in a computational model to simulate choices between a safe and a two-outcome prospect.
By proposing distinct links between the parameter capturing different sampling strategies, the resulting choices, and the estimated CPT parameters, the simulation substantiates the core claim of this paper, namely, that sampling effects on choices in DfE may not be reduced to the overall number of sampled outcomes.
That is, the simulation demonstrates how the overall number of sampled outcomes can increase without the underweighting of rare outcomes fading, assuming that the sampling strategy translates this increase in overall number into a greater number of samples over which evidence is accumulated, but not samples of greater size.
The last section supplements the rather technical inquiry into the sampling process and its consequences with a theoretical inroad into the question how the idea of sampling strategies can be integrated into the broader study of the computationally limited mind as an adaptive cognitive system.
The paper closes with a summary and a conclusion.
Note that this paper, including the simulations and data analyses, is reproducible---materials and instructions can be found on the GitHub repository.

@@

To begin with, let the axiomatic definition of a prospect be that of a discrete random variable's distribution [see @tverskyAdvancesProspectTheory1992].
Let therefore the tuple $(\Omega, \mathcal{F}, P)$ be a probability space. 
Following the @kolmogorovFoundationsTheoryProbability1950 axioms and the notation of @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, $\Omega$ is the sample space containing a finite set of elements, one of which results from choosing the respective prospect:
$$
\omega_i \in \{\omega_1, ..., \omega_n\} = \Omega
\; .
\tag{2}
$$ 
$\mathcal{F}$ is the set of all possible subsets of $\Omega$, i.e., the power set $\mathcal{P}(\Omega)$, where each element $A \in \mathcal{P}(\Omega) = \mathcal{F}$ is a subset of $\Omega$.^[<!--Open footnote-->Note that this paper considers only the case of finite sample spaces. The exact axiomatic definition of $\mathcal{F}$, which can be found in Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, pp. 2-3 and 14-15], also covers infinite sample spaces and is that of a $\sigma$-algebra. For the finite case, however, $\mathcal{P}(\Omega)$ can be considered as such [@georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1.1].<!--Close footnote-->]
$P$ is a probability measure
$$
P: \mathcal{F} \to [0,1]
\; ,
\tag{3}
$$
which assigns each subset $A \in \mathcal{F}$ a probability $0 < p(A) \leq 1$ with $P(\Omega) = 1$.<!--^[The probabilities $p(\omega)$ are determined by the probability mass function $p : \Omega \to [0,1]$, which is used to construct the probability measures $P(A) = \sum_{\omega \in A} p(\omega)$ for all $A \in \mathcal{F}$.]-->
According to Kolmogorov [-@kolmogorovFoundationsTheoryProbability1950, p. 21-22],^[<!--Open footnote-->See also @georgiiStochastikEinfuhrungWahrscheinlichkeitstheorie2015, Chapter 1, for a comprehensive yet accessible introduction to random variables.<!--Close footnote-->]
the random variable $X$ is the measure
$$
\begin{aligned}
  X : (\Omega, \mathcal{F}) &\to (\Omega', \mathcal{F'})  \\
  \omega &\mapsto x
  \; ,
\end{aligned}
\tag{4}
$$
where $(\Omega', \mathcal{F'})$ is a measurable space with each element $x \in \Omega'$ being a possible outcome of a prospect and each element $A' \in \mathcal{F'}$ being a subset of $\Omega'$.
An outcome's probability $p_X(x)$ is then provided by the pushforward probability measure
$$
P_X : \mathcal{F'} \to [0,1]
\tag{5}
$$
with 
$$
P_X(A' \in \mathcal{F'}) := P(X^{-1} \ A') = P(\{\omega: X(\omega) = x \in A'\})
\; .
\tag{6}
$$
That is, the set consisting of a single outcome $x$ is a subset $\{x\} \in \mathcal{F'}$ and we therefore obtain $p_X(x) = P(\{\omega : X(\omega) = x \in \{x\}\})$.
Note that the probability measure in (5) and (6), respectively, is a discrete random variable's distribution and therefore a prospect.
To summarize and simplify, given a choice between $1, ..., k$ prospects, the inputs from the environment or memory should provide information about the set
$$
C = \{P_{X_1}, ... , P_{X_k}\}
\tag{7}
$$
with each element $c \in C$ being a distribution $P_X$ of a random variable defined on its own probability space.
Accordingly, each $c$ can itself be considered a set of outcome-probability pairs $(x_i, p_X(x_i)) \in \{(x_1, p_X(x_1)), ..., (x_n, p_X(x_n))\}$.

However, only occasionally in peoples' daily life, inputs take the form of explicit descriptions of all outcome-probability pairs.
In such cases, people would make DfD, since the information from which the mind learns about the properties of prospects are complete descriptions thereof.
Yet, rather often, people make DfE, where the mind can learn about the latent properties of prospects only by experiental sampling over time [@hertwigDescriptionexperienceGapRisky2009, p. 517].
Accordingly, considering the sampling paradigm,^[<!--Open footnote-->Note that it has been emphasized that in the natural world samples are "virtually never random" [@fiedlerBewareSamplesCognitiveecological2000, p. 660]. See, e.g., @plonskyRelianceSmallSamples2015, who drop the i.i.d.-assumption for DfE.<!--Close footnote-->] 
let a sample of a prospect be a set of realizations of the respective random variable.
More specifically, for the choice between $1, ..., k$ prospects, the inputs to DfE---i.e., the sampled outcomes---are generated by a set $S$ of prospect-specific discrete-time stochastic processes
$$
S = \{\{X_{1t}\}, ... , \{X_{kt}\}\}
\; ,
\tag{8}
$$
where each $s \in S$ is a sequence of independent and identically distributed (i.i.d.) random variables, each $t \in \{t_1, ..., t_N\}$ corresponds to the position of the respective random variable in such a sequence, and $N$ denotes the length of the respective sequence, which corresponds to the overall number of sampled outcomes for this prospect.
Now, one core assumption of this paper is that, for a stochastic process $s \in S$ of length $N$, the mind sequentially integrates the sampled outcomes into either one enumerated sample growing to the size $N$ or into multiple smaller enumerated samples, each corresponding to a unique sub-sequence of s.
Assuming that the mind uses all samples so obtained during a process of evidence accumulation, this paper discusses and demonstrates how different sampling strategies that alter the number and size of these samples can produce distinct choice patterns in DfE.
Before so doing, however, the following section reviews how CPT can be used as a data model that captures systematic deviations from the principle of mathematical expectation in the parameter estimates of a *value* and a *weighting function*.

@@

To demonstrate the impact of different sampling strategies on the inferences about the latent properties of prospects and the resulting choices in DfE, a simulation study was conducted.
Therefore, computational models were implemented that generate and integrate samples from prospects according to varying parameters reflecting different sampling strategies.

## Choice Problems

We test a set of 2-prospect choice problems, where one of the prospects contains a safe outcome, i.e., $p(\omega) = 1$ and the other two outcomes where all $p(\omega) \neq 1$.
Both outcomes and probabilities are drawn from uniform distributions, ranging from 0 to 20 for outcomes and from .01 to .99 for probabilities of the smaller outcome of the risky prospect.
To omit dominant prospects within a choice problem, outcomes of the safe prospect always fall between both outcomes of the risky prospect.
Table A1 in contains the test set of 60 choice problems, which were sampled from an initial set of 10,000.
Sampling of gambles was stratified, randomly drawing an equal number of 20 gambles with no, an attractive, and an unattractive rare outcome.
Risky outcomes are considered *"rare"* if their probability is $p < .2$ and *"attractive"* (*"unattractive"*) if they are higher (lower) than the safe outcome.

For each parameter combination of the generating model, 100 synthetic agents are presented with 60 choices problems.
In sum, 100 (parameter combinations) x 100 (agents) x 60 (choices) = 600,000 choices are simulated.

## Data Generation

@@

## Results

@@

@@

# Discussion
